Lattices of acyclic pipe dreams

### 2023-03-16 acyclicFacets/draft/latticePipeDreams.tex
change congruence to equivalence

\begin{conjectureA}
\label{conj:A}
If~$Q$ is alternating, then the subword complex congruence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
\end{conjectureA}

@@

\begin{definition}
\label{def:pipeDreamCongruenceSubwordComplexes}
For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex congruence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ of linear extensions of strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
\end{definition}

\nantel{it is bad to name this ``congruence". Call it equivalence, and state it is a concruence in the conjecture.}

@@

Despite its name, this equivalence relation is not always a congruence because of Issue~(ii) above.
To fix it, we now assume that the word~$Q$ is \defn{alternating}, meaning that all non-commuting pairs $s, t\in S$ alternate within $Q$ (this notion was already considered in \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
This enables us to state our first conjecture, intended to extend~\cref{thm:pipeDreamCongruence}.

\begin{conjecture}
\label{conj:latticeCongruenceAlternating}
For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the subword complex congruence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
\end{conjecture}

>>>>

\begin{conjectureA}
\label{conj:A}
If~$Q$ is alternating, then the subword complex equivalence~$\equiv_{Q, \omega}$ is a lattice congruence of the interval~$[e, \omega]$ of the weak order.
\end{conjectureA}

@@

\begin{definition}
\label{def:pipeDreamCongruenceSubwordComplexes}
For a non-empty subword complex $\subwordComplex(Q,\omega)$, the \defn{subword complex equivalence} is the equivalence relation~$\equiv_{Q,\omega}$ on the interval~$[e, \omega]$  whose equivalence classes are the sets~$\strongLinearExtensions(I)$ of linear extensions of strongly acyclic facets~$I$ of~$\subwordStronglyAcyclicFacets(Q, \omega)$.
In other words, $\pi \equiv_{Q,\omega} \pi'$ if and only if $\pi$ and $\pi'$ are linear extensions of the same facet.  
\end{definition}

@@

The subword complex equivalence is not always a congruence because of Issue~(ii) above.
To fix it, we now assume that the word~$Q$ is \defn{alternating}, meaning that all non-commuting pairs $s, t\in S$ alternate within $Q$ (this notion was already considered in \cite{PilaudSantos-brickPolytope, CeballosLabbeStump}).
This enables us to state our first conjecture, intended to extend~\cref{thm:pipeDreamCongruence}.

\begin{conjecture}
\label{conj:latticeCongruenceAlternating}
For a non-empty subword complex $\subwordComplex(Q,\omega)$ where~$Q$ is alternating, the subword complex equivalence~$\equiv_{Q,\omega}$ is a lattice congruence of the interval~$[e,\omega]$ of the weak order.
\end{conjecture}
